{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-12 thesis/quicksand.tex
fix stray revision cmd in quicksand pasta

% TODO smae as above
\begin{figure}[t]
	\begin{tabular}{rll}
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{publish(x);} & \\
		2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		3 & \texttt{\hilight{olivegreen}{free}(x);} \\
		4 & & \texttt{x2 = get\_published\_x();} \\
		5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
		6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
	\end{tabular}
	\caption{If a single-pass \revision{Limited HB analysis}~discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
	\label{fig:recycle-bug}
\end{figure}

>>>>

% TODO smae as above
\begin{figure}[t]
	\begin{tabular}{rll}
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{publish(x);} & \\
		2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		3 & \texttt{\hilight{olivegreen}{free}(x);} \\
		4 & & \texttt{x2 = get\_published\_x();} \\
		5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
		6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
	\end{tabular}
	\caption{If a single-pass Limited HB analysis discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
	\label{fig:recycle-bug}
\end{figure}
